BCOV theory on a complex surface

### 2018-06-19 2d_bcov.tex
2d bcov

\begin{document}
\maketitle
\tableofcontents

Suppose $X$ is a complex manifold of complex dimension $2$. equipped with a holomorphic symplectic form $\omega \in \Omega^{2,hol}(X)$.
We study BCOV theory on $X$, which should be thought of as the theory of ``divergence-free holomorphic polyvector fields" with respect to the fixed symplectic structure.

@@

There is a related Lie algebra of holomorphic {\em Hamiltonian} vector fields. 
This Lie algebra has underlying vector space the space of holomorphic functions $\sO^{hol}(X)$ and is equipped with Lie bracket given by the holomorphic Poisson bracket $\{-,-\}_\omega$. 
As we've done several times already, this Lie algebra admits a Dolbeualt resolution as a dg Lie algebra 
\be\label{hamiltonian}
\left(\Omega^{0,*}(X), \dbar, \{-,-\}_\omega \right).
\ee

@@

Given any dg Lie algebra, there is a standard construction to define a classical BV theory.

The fields are
\ben
(A, B) \in \Omega^{0,*}(X) [1] \oplus \Omega^{2,*}(X) 
\een
The action functional is
\ben
\int_X B \dbar A + \frac{1}{2} \int_X B \{A, A\} .
\een
6
\end{document}

>>>>

\begin{document}
\maketitle
%\tableofcontents

Suppose $X$ is a complex manifold of complex dimension $\dim_\CC(X) = 2$ equipped with a holomorphic symplectic form $\omega \in \Omega^{2,hol}(X)$.
We study BCOV theory on $X$, which should be thought of as the theory of ``divergence-free holomorphic polyvector fields" with respect to the volume form determined by the fixed symplectic structure.

@@

There is a related Lie algebra of holomorphic {\em Hamiltonian} vector fields. 
This Lie algebra has underlying vector space the space of holomorphic functions $\sO^{hol}(X)$ and is equipped with Lie bracket given by the holomorphic Poisson bracket $\{-,-\}_\omega$ determined by the symplectic form $\omega$. 
As we've done several times already, this Lie algebra admits a Dolbeualt resolution as a dg Lie algebra 
\be\label{hamiltonian}
\left(\Omega^{0,*}(X), \dbar, \{-,-\}_\omega \right).
\ee

@@

Given any dg Lie algebra, there is a standard construction to define a classical BV theory. \brian{cotangent theory}

The fields are
\ben
(A, B) \in \Omega^{0,*}(X) [1] \oplus \Omega^{2,*}(X) 
\een
The action functional is
\be\label{action3}
\int_X B \dbar A + \frac{1}{2} \int_X B \{A, A\} .
\ee

The following lemma is an immediate consequence of our discussion.

\begin{lem} 
The action functional (\ref{action2}) is equivalent to the action functional (\ref{action3}).
In other words, BCOV theory on a complex surface is equivalent to the cotangent theory associated to the Lie algebra of holomorphic symplectic vector fields.
\end{lem}

\end{document}
